### 2014-10-29 motivation.tex
example

A key novelty	in \name is that it allows the addition of new RDTs to the store,
immensely improving the programmability of data stores. The programmer no
longer has to coerce the application logic to utilize the store provided data
types. In addition, \name treats the convergence semantics of the data type
separately from the consistency properties. The separation of concern allows
the programmer to \emph{operationally} reason about conflict resolution, while
permitting \emph{declarative} reasoning for consistency. As mentioned in the
previous section, RDTs are described in terms of operations on a RDT object,
where each operation is described as a reduction over the state of the object
i.e., the list of effects. Let us assume that the bank account object provides
three operations: \cf{deposit}, \cf{withdraw} and \cf{getBalance}, with the
assumption that the withdraw fails if the account has insufficient balance.
Every operation in \name is of the following type, written in Haskell syntax:

@@

\noindent It takes a list of effects (the \emph{context} for the operation), an
argument and returns a result along with an optional effect. Read-only
operations do not return any effect. If an effect is returned, it is added to
the state of the object at the current replica, and asynchronously sent to
other replicas. The implementation of the bank account operations is given
below:

>>>>

A key novelty of \name is that it allows the addition of new RDTs to the
store, greatly improving programmability.  Specifically, programmers no
longer have to coerce application logic to conform to to store-provided data
types. In addition, \name treats the convergence semantics of the data type
separately from consistency properties. This separation of concerns allows
the programmer to \emph{operationally} reason about conflict resolution,
while permitting \emph{declarative} reasoning for consistency. As mentioned
in the previous section, RDTs are described in terms of operations on a RDT
object, where each operation is described as a reduction over the state of
the object i.e., the list of effects.

Assume that the bank account object provides three operations: \cf{deposit},
\cf{withdraw} and \cf{getBalance}, with the assumption that the \cf{withdraw}
fails if the account has insufficient balance.  Every operation in \name is
of the following type, written in Haskell syntax:

@@

\noindent An operation takes a list of effects (the \emph{context} for the operation), an
argument and returns a result along with an optional effect. Read-only
operations do not return any effect. If an effect is returned, it is added to
the state of the object at the current replica, and asynchronously sent to
other replicas. The implementation of the bank account operations is given
below:
